%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

    %---------------------------------------------------------
    \cventry
    {Researcher} % Job title
    {ZEW -- Leibniz Centre for European Economic Research} % Organization
    {Mannheim, Germany} % Location
    {Dec 2020 - Present} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Analyzing the impacts of climate and energy policy, in particular carbon pricing, in European.}
            \item {Analyzing climate change and energy transition risks.}
            \item {Writing academic papers and policy briefs.}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Research Affiliate} % Job title
    {Yale University} % Organization
    {New Haven, CT, USA} % Location
    {Aug 2017 - Present} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Collaborating with researchers for projects regarding energy transitions and environmental impacts.}
            \item {Supporting Ph.D. students and postdoctoral researchers to conduct scenario analyses of energy and climate policies using the National Energy Modeling System (NEMS).}
            \item {Publishing manuscripts in academic journals.}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Postdoctoral Research Associate} % Job title
    {Yale University} % Organization
    {New Haven, CT, USA} % Location
    {Jul 2017 - Jul 2020} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Designed macroeconomic scenarios of low-carbon energy transitions, including intensive energy efficiency improvements, abundant natural gas supply, electrifying transportation, decreased costs of distributed generation, and carbon pricing policy.}
            \item {Analyzed large energy, emissions, climate, and health datasets.}
            \item {Implemented and developed a Yale version of the NEMS model, a large-scale energy-economic general equilibrium model.}
            \item {Presented research in conferences and policy meetings.}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Quantitative Analyst} % Job title
    {S\&P Global Platts} % Organization
    {London, UK} % Location
    {Nov 2016 - Jun 2017} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Developed econometric and statistical models for forecasting energy demand.}
            \item {Initiated and developed new modeling framework, integrating SQL and R.}
            \item {Contributed to new market offerings -- short-term energy market forecasts.}
            \item {Conducted data analyses of fundamentals and prices for natural gas markets.}
            \item {Created data visualization tools for market analysis.}
            \item {Wrote short-term and long-term market reports.}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Modeling Analyst} % Job title
    {Aurora Energy Research} % Organization
    {Oxford, UK} % Location
    {Aug 2015 - Nov 2016} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Lead the development of large-scale economic models for the global natural gas markets.}
            \item {Initiated new product offerings, the analytics of global natural gas market.}
            \item {Developed a new modeling framework, integrating R, Python, SQL, Tableau, and GAMS.}
            \item {Documented model development history using the version control tool, Git.}
            \item {Created and maintained a geospatial energy transit dataset.}
            \item {Conducted scenario analyses for the European natural gas markets and infrastructure development.}
            \item {Created data visualization tools for the research team, facilitating report writing and market analyses.}
            \item {Provided training sessions of quantitative methods for colleagues.}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Tom Slick Research Fellow} % Job title
    {Texas A\&M University} % Organization
    {College Station, TX, USA} % Location
    {Jan 2015 - Aug 2015} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Funded by the Tom Slick Graduate Research Fellowship Program at Texas A\&M University.}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Research Assistant} % Job title
    {Texas A\&M University} % Organization
    {College Station, TX, USA} % Location
    {Jan 2012 - Dec 2014} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Developed statistic, econometrics, and economic models to evaluate the impact of climate variability on agriculture.}
            \item {Built an integrated assessment model for natural resource management.}
            \item {Collaborated with economists, biologists, and policymakers.}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Course Instructor} % Job title
    {Texas A\&M University} % Organization
    {College Station, TX, USA} % Location
    {Fall 2013 \& 2014} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Taught Applied Mathematical Programming in GAMS.}
            \item {Teaching evaluations: 4.90/5.00 (Fall 2014); 4.34/5.00 (Fall 2013).}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Teaching Assistant} % Job title
    {Texas A\&M University} % Organization
    {College Station, TX, USA} % Location
    {Spring 2012 \& 2015} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Assisted in teaching Agribusiness Management and Environmental \& Natural Resource Economics.}
        \end{cvitems}
    }

    %---------------------------------------------------------
\end{cventries}
