%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\cvsubsection{Academic Papers}


\begin{pubitems} % Description(s)
	\item {Gillingham, K., \textbf{P. Huang}, C. Buehler, J. Peccia, and D. R. Gentner. 2021. The Climate and Health Benefits from Intensive Building Energy Efficiency Improvements. \textit{Science Advances}. 7, eabg0947. (Media: \href{https://environment.yale.edu/news/article/efficient-buildings-could-save-thousands-of-lives-in-us-every-year/}{YSE News, Aug 20, 2021}). \href{https://advances.sciencemag.org/content/7/34/eabg0947}{Paper Link}}
    \item {Gillingham, K. and {\bf P. Huang}. 2020. Long-Run Environmental and Economic Impacts of Electrifying Ports in the United States. \textit{Environmental Science \& Technology}. 54(16), 9824--9833. (Media: \href{https://www.nature.com/articles/s43017-020-0090-6}{Nature Reviews Earth \& Environment, Aug 6, 2020}). \href{https://www.dropbox.com/s/0g1fmsu6kdwhhhg/GillinghamHuang_EST2020.pdf?dl=0}{Paper Link}}
    \item {Gillingham, K. and {\bf P. Huang}. 2019. Is Abundant Natural Gas a Bridge to a Low-carbon Future or a Dead-end?. \textit{Energy Journal}. 40(2), 1--26. (Media: \href{https://www.denverpost.com/2020/01/31/colorado-natural-gas-bridge-fuel-wind-solar-xcel-tri-state/}{The Denver Post, Jan 31, 2020}). \href{https://www.iaee.org/en/Publications/ejarticle.aspx?id=3325}{Paper Link}}
    \item {Wilberg, M.J., R.T. Woodward, {\bf P. Huang}, and D. Tomberlin. 2019. Developing Precautionary Reference Points for Fishery Management Using Robust Control Theory: Application to the Chesapeake Bay Blue Crab Fishery. \textit{Marine and Coastal Fisheries} 11(2), 177-188.}
    \item {Fernandez, M., {\bf P. Huang}, B.A. McCarl, and V. Mehta. 2016. Value of Decadal Climate Variability Information for Agriculture in the Missouri River Basin. \textit{Climatic Change}. 139(3--4), 517--533.}
    \item {\textbf{Huang, P.} 2015. An Inverse Demand System for the Differentiated Blue Crab Market in Chesapeake Bay. {\itshape Marine Resource Economics} 30(2):139--156.}
    \item {\textbf{Huang, P.}, R.T. Woodward, M.J. Wilberg, and D. Tomberlin. 2015. Management Evaluation for the Chesapeake Bay Blue Crab Fishery: An Integrated Bioeconomic Approach. {\itshape North American Journal of Fisheries Management} 35(2):216--228. (Selected as Best Paper Award for the journal in 2015)}
\end{pubitems}


%---------------------------------------------------------
\cvsubsection{Working Papers}

\begin{pubitems} % Description(s)
    \item {Racial Disparities in the Health Effects from Air Pollution: Evidence from Ports (with Kenneth Gillingham), \href{https://www.nber.org/papers/w29108}{NBER Working Paper}, \href{https://www.zew.de/publikationen/racial-disparities-in-the-health-effects-from-air-pollution-evidence-from-ports}{ZEW Discussion Paper}}
\end{pubitems}


%---------------------------------------------------------
\cvsubsection{Public Outreach}


\begin{pubitems} % Description(s)
    \item {Shipping Shapes Health, \textit{Public Health Post}, February 3, 2021. \href{https://www.publichealthpost.org/research/shipping-shapes-health/}{Article Link}}
\end{pubitems}

